New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations

### 2019-12-31 nontex/install/git/fs_git_setup.Rmd
bash file for git pull and push

1. start ssh-agent secure session
2. pull from multiple Repositories upon start of working session.
3. commit changes as work on one computer
4. upon leaving a computer with commited changes, push all

@@

>>>>

1. start ssh-agent secure session
2. pull from multiple Repositories upon start of working session.
3. commit changes as work on one computer
4. upon leaving a computer with commited changes, push all
5. create bash file to make it easier to repeat steps

@@

to create bash file to store these (from git bash in windows):

```{bash}
# store bash file in ~\PyFan\bin
mkdir ~/PyFan/bin
cd ~/PyFan/bin

# create bash file
vim pull_repos
vim push_repos

# paste the text below over, comfirm bash loc with: which bash
#!/usr/bin/bash
echo start fan github pull
# Security
eval "$(ssh-agent)"
ssh-add ~/.ssh/id_rsa
# Pull from Persistent Repos
cd ~/fanwangecon.github.io
git pull github master
# Stop Secured SSH
kill $SSH_AGENT_PID

# change permission to make file an executable
chmod u+x ~/PyFan/bin/pull_repos
chmod u+x ~/PyFan/bin/push_repos
# execute script
bash ~/PyFan/bin/pull_repos
```

### 2019-12-31 nontex/install/windows/fn_installations.Rmd
vim goyo limelight and other colors tests
bash file for git pull and push

1. install hydrogen in atom. Follow [instructions](http://nteract.io/atom).
    - terminal in windows or linux after installation: *apm install hydrogen*
    - apm is the atom package manager.
2. go to the programs above and try to run.

```{bash}
# Once atom is installed, can use apm to install packages
apm install hydrogen
# Inside Conda open up atom
atom
# open up any py from from within, try 1+1, does it work?
# also use script, try ctrl + shift + b, run whole file (not hydrogen)
```

@@

>>>>

1. install hydrogen in atom. Follow [instructions](http://nteract.io/atom).
    - terminal in windows or linux after installation: *apm install hydrogen*
    - apm is the atom package manager.
2. Pull/Sync with Git and open mulitple projects in atom, follow [guide here](https://fanwangecon.github.io/Tex4Econ/nontex/install/git/fs_git_setup.html).
3. go to the programs above and try to run.

```{bash}
# Once atom is installed, can use apm to install packages
apm install hydrogen
apm install project-manager
# Inside Conda open up atom
atom
# open multiple projects from atom at the same time, after repos synced
atom ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ
# open up any py from from within, try 1+1, does it work?
# also use script, try ctrl + shift + b, run whole file (not hydrogen)
```

@@

## Package Managers

- [scoop](https://github.com/lukesampson/scoop/wiki/Quick-Start)

```
# in powershell
# enter cmd
# type powershell in cmd to enter powershell from cmd
powershell
# permission
set-executionpolicy remotesigned -scope currentuser
# install
iwr -useb get.scoop.sh | iex
```
